Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-27 paper.tex
Add Component - blind signature

\subsubsection{blind signature}

>>>>

\subsubsection{Blind Signature}
Blind signature\cite{blindSig} is a form of digital signature where the message is blinded before it is signed, and the resulting blind signature can be verified publicly against the original. To perform such a signature, the message is first "blinded" by a random "blinding factor", then passed to a signer to sign. The resulting message, along with the blinding factor, can be later verified with the signer's public key. In our system design, brokers would perform blind signature during the process of adding new products for data providers, in order to upload the secret key of MAM channel to smart contract without knowing it. Furthermore, only one blind-signatured secret key is valid for trading and it is not allowed to be updated. By putting the secret key on smart contract prevents malicious providers trades invalid secret keys to consumers privately.
